---
title: "FastQC Analysis Report"
output: pdf_document
params:
  filename: NA
  read_R1: NA
  filename_R1: NA
  file_type_R1: NA
  encoding_R1: NA
  total_sequences_R1: NA
  total_bases_R1: NA
  poor_quality_R1: NA
  sequence_length_R1: NA
  per_base_quality_R1: NA
  per_sequence_quality_R1: NA
  per_base_sequence_content_R1: NA
  per_base_n_content_R1: NA
  sequence_length_distribution_R1: NA
  duplication_levels_R1: NA
  
  read_R2: NA
  filename_R2: NA
  file_type_R2: NA
  encoding_R2: NA
  total_sequences_R2: NA
  total_bases_R2: NA
  poor_quality_R2: NA
  sequence_length_R2: NA
  per_base_quality_R2: NA
  per_sequence_quality_R2: NA
  per_base_sequence_content_R2: NA
  per_base_n_content_R2: NA
  sequence_length_distribution_R2: NA
  duplication_levels_R2: NA
---

## File
- **FastQC Folder:** `r params$filename`

## Reference – Read R1
- **Read**: `r params$read_R1`  
- **Filename**: `r params$filename_R1`  
- **File type**: `r params$file_type_R1`  
- **Encoding**: `r params$encoding_R1`  
- **Total sequences**: `r params$total_sequences_R1`  
- **Total bases**: `r params$total_bases_R1`  
- **Poor quality reads**: `r params$poor_quality_R1`  
- **Sequence length**: `r params$sequence_length_R1`  

## Reference – Read 2
- **Read:** `r params$read_R2`
- **Filename:** `r params$filename_R2`
- **File Type:** `r params$file_type_R2`
- **Encoding:** `r params$encoding_R2`
- **Total Sequences:** `r params$total_sequences_R2`
- **Total Bases:** `r params$total_bases_R2`
- **Poor Quality Reads:** `r params$poor_quality_R2`
- **Sequence Length:** `r params$sequence_length_R2`


## Per Base Quality
### Read R1
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$per_base_quality_R1)
```

### Read R2
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$per_base_quality_R2)
```


## Per Sequence Quality
### Read R1
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$per_sequence_quality_R1)
```

### Read R2
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$per_sequence_quality_R2)
```


## Per Base Sequence Content
### Read R1
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$per_base_sequence_content_R1)
```

### Read R2
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$per_base_sequence_content_R2)
```


## Per Base N Content
### Read R1
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$per_base_n_content_R1)
```

### Read R2
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$per_base_n_content_R2)
```


## Sequence Length Distribution
### Read R1
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$sequence_length_distribution_R1)
```

### Read R2
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$sequence_length_distribution_R2)
```


## Duplication Levels
### Read R1
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$duplication_levels_R1)
```

### Read R2
```{r echo=FALSE, out.width="80%"}
knitr::include_graphics(params$duplication_levels_R2)
```
