---
title: "VCF Analysis Report"
output: pdf_document
  
params:
  file_name: NA
  selected_chromosome: NA
  mutation_donut: NA
  mutation_distribution: NA
  snp_value: NA
  snp_types_donut: NA
  snp_class_stacked: NA
  snp_class_boxplot: NA
  snp_class_barplot: NA
  indel_values: NA
  indel_length_avg: NA
  indel_length_med: NA
  indel_types: NA
  indel_stacked: NA
  indel_length: NA
  indel_length_boxplot: NA
  quality_avg: NA
  quality_med: NA
  quality_bar: NA
  quality_on_chroms: NA
  allele_freq_avg: NA
  allele_freq_med: NA
  allele_freq_hexbin: NA
  allele_freq_on_chroms: NA
  read_depth_avg: NA 
  read_depth_med: NA
  read_depth_density: NA
  read_depth_on_chroms: NA
---

## File

-   **File:** `r params$file_name`
-   **Selected chromosome:** `r params$selected_chromosome`

## Mutation Counts

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$mutation_donut)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$mutation_distribution)
```

## Single Nucleotide Polymorphism (SNP) Analysis

-   `r params$snp_value`

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$snp_types_donut)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$snp_class_stacked)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$snp_class_boxplot)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$snp_class_barplot)
```

## Insertion and Deletion (INDEL) Analysis

-   `r params$indel_values`
-   `r params$indel_length_avg`
-   `r params$indel_length_med`

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$indel_types)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$indel_stacked)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$indel_length)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$indel_length_boxplot)
```

## Quality Analysis

-   `r params$quality_avg`
-   `r params$quality_med`

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$quality_bar)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$quality_on_chroms)
```

## Allele Frequency Analysis

-   `r params$allele_freq_avg`
-   `r params$allele_freq_med`

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$allele_freq_hexbin)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$allele_freq_on_chroms)
```

## Read Depth Analysis

-   `r params$read_depth_avg`
-   `r params$read_depth_med`

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$read_depth_density)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
print(params$read_depth_on_chroms)
```
